%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Open Source Contributions}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Defining, solving, and simulating Markov Decision Processes in Julia} % Position
    {
    \hrefs{https://github.com/JuliaPOMDP/POMDPs.jl}{POMDPs.jl}
    } % Project
    {Contributor} % Location
    {Julia} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Contributor of \hrefs{https://github.com/JuliaPOMDP/MCTS.jl}{MCTS.jl}, a Monte-Carlo tree search package for solving Markov Decision Processes.}
        \item {Found and fixed bugs in MCTS.jl implementation. Fixed and improved the docs and examples.}
        \item {Found and fixed performance performance issues in the POMDPs.jl ecosystem.}
        \item {Found and fixed issues in docs and examples across POMDPs.jl.}
        \item {Led a student project that added a finite horizon MDP solver to the POMDPs.jl ecosystem.}
      \end{cvitems}
    }
    
%---------------------------------------------------------
  \cventry
    {Tool for (lazy) visualization of large trees} % Position
    {\hrefs{https://github.com/sisl/D3Trees.jl}{sisl/D3trees.jl}} % Project
    {Contributor} % Location
    {Julia/JavaScript} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item{Rewrote the package as Julia server - Javascript client.}
        \item{Implemented a selective lazy visualization of very large tree-like data structures.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fast offline reverse geocoder in Julia}
    {\hrefs{https://github.com/BoZenKhaa/ReverseGeocode.jl}{ReverseGeocode.jl}}
    {Maintainer}
    {Julia} 
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Replicates functionality of reverse-geocode python package.}
        \item {I created this project to learn about creating Julia packages and CI/CD pipelines in Github.}
      \end{cvitems}
    }

% %---------------------------------------------------------
  \cventry
    {Repository for a public mobility dataset}
    {\hrefs{https://github.com/aicenter/Ridesharing_DARP_instances}{Ridesharing\_DARP\_instances}}
    {Contributor}
    {Python} 
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Prepared README.md and other online presentations of the code and dataset.}
        \item {Created a CLI runner for quickly running and re-running benchmarks on a cluster.}
      \end{cvitems}
    }

%   \cventry
%     {Simple CLI mailer for processing membership fee payments} % Course
%     {\hrefs{https://github.com/BoZenKhaa/platby}{platby}} % Course
%     {Maintainer, Main Contributor} % Location
%     {Python} % Date(s)
%     {
%       \begin{cvitems} % Description(s) bullet points
%         \item {Implemented connection to the Google sheets and Gmail API}
%         \item {Implemented data processing as required by the organization}
%         \item {Implemented email generation with QR codes}
%       \end{cvitems}
%     }

%---------------------------------------------------------

\end{cventries}
    

% %---------------------------------------------------------
% \cvsubsection{Reports}
% % %---------------------------------------------------------

% \begin{cvpubs}
%     \cvpub{\textbf{Cuchý, M}, Fiedler, D, Mrkos, J, Vokřínek, J.  2021. Feasibility of VTOL Transport in Urban Environments. Bell Textron Multi-Modal Traveler Modeling Project.}

%     \cvpub{\textbf{Mrkos, J}, Drchal, J, Egan, M, Jakob, M.  2016. Liftago On-Demand Transport Dataset and Market Formation Algorithm Based on Machine Learning. Liftago Market Formation Project. Available at \href{https://arxiv.org/abs/1608.02858}{arXiv:1608.02858}.}
% \end{cvpubs}

% % %---------------------------------------------------------
