%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD Thesis project} % Position
    {Automated Marketplaces for Transportation Systems} % Project
    {CTU in Prague} % Location
    {ongoing} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Thesis aims to apply MDP heuristic methods to a new MDP formulation of a network revenue management dynamic pricing problems in order to quickly solve large problem instances.}
        \item {The methods will be evaluated on artificial, as well as realistic problem instances based on web-scraped dataset of bus ticket sales and EV charging sessions.}
        \item {Currently, I am preparing a final journal publication and compiling the thesis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Bell Textron Inc. Multi-Modal Traveler Modeling Project} % Position
    {\href{https://www.aic.fel.cvut.cz/projects/passenger-decision-modeling-in-a-multi-modal-urban-environment}{Feasibility of eVTOL Transport in Urban Environments}} % Project
    {CTU in Prague} % Location
    {2021} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Development of a multi-modal simulator to determine viability of electric vertical take-off and landing travel system when compared to classical modes of travel.}
        \item {Definition and clarification of the project goals with the customer, coordination of work within the CTU team.}
        \item {Preparation of final deliverable, including codebase. }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Horizon 2020 international project} % Course
    {\href{https://electrific-project.eu/}{Electrific Project}} % Course
    {Five EU countries} % Location
    {2015-2019} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Development of solution for pricing of EV charging sessions using charging demand, energy availability and greenness of energy.}
        \item {Integration and coordination with other members of the multi-national project, presentation of concepts and solutions, contribution to project deliverables.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://www.liftago.com/}{Liftago - major Czech Mobility-on-Demand provider}} % Position
    {\href{https://cw.fel.cvut.cz/b221/courses/b4b33rph/start}{Data-driven market formation algorithm for Liftago}} % Course
    {CTU in Prague} % Location
    {2015-2016} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Development of a market formation REST API based on customer needs.}
        \item {Data analysis, preparation of ML models.}
        \item {Preparation of brief technical report \href{https://arxiv.org/abs/1608.02858}{arXiv:1608.02858}.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
    

% %---------------------------------------------------------
% \cvsubsection{Reports}
% % %---------------------------------------------------------

% \begin{cvpubs}
%     \cvpub{\textbf{Cuchý, M}, Fiedler, D, Mrkos, J, Vokřínek, J.  2021. Feasibility of VTOL Transport in Urban Environments. Bell Textron Multi-Modal Traveler Modeling Project.}

%     \cvpub{\textbf{Mrkos, J}, Drchal, J, Egan, M, Jakob, M.  2016. Liftago On-Demand Transport Dataset and Market Formation Algorithm Based on Machine Learning. Liftago Market Formation Project. Available at \href{https://arxiv.org/abs/1608.02858}{arXiv:1608.02858}.}
% \end{cvpubs}

% % %---------------------------------------------------------
