%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------

%---------------------------------------------------------
\cvsubsection{Published}
%---------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Cuchý, M}, Jakob, M, Mrkos, J. 2024. Route and Charging Planning for Electric Vehicles: A Multi-Objective Approach. Transportation Letters, published \hrefs{https://doi.org/10.1080/19427867.2024.2315359}{online}.}
    
    \cvpub{\textbf{Fiedler, D}, Mrkos, J, 2023. Large-scale Ridesharing DARP Instances Based on Real Travel Demand. Presented at the 26th IEEE International Conference on Intelligent Transportation Systems (ITSC 2023). Preprint at \hrefs{https://arxiv.org/abs/2305.18859}{arXiv:2305.18859}.}

    \cvpub{\textbf{Mrkos, J}, Basmadjian, R. 2022. Dynamic Pricing for Charging of EVs with Monte Carlo Tree Search. Smart Cities, \hrefs{https://doi.org/10.3390/smartcities5010014}{5(1): 223-240}.}

    \cvpub{\textbf{Basmadjian, R}, Mrkos, J, Kirpes, B, Cuchý, M.  2020. A Reference Architecture for Interoperable Reservation Systems in Electric Vehicle Charging. Smart Cities, \hrefs{https://doi.org/10.3390/smartcities3040067}{3(4): 1405-1428}.}

    \cvpub{\textbf{Schaefer, M}, Čáp, M, Mrkos, J, Vokřínek, J.  2019. Routing a Fleet of Automated Vehicles in a Capacitated Transportation Network. 2019 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), \hrefs{http://dx.doi.org/10.1109/IROS40897.2019.8967723}{8223-8229}.}

    \cvpub{\textbf{Basmadjian, R}, Kirpes, B, Mrkos, J, Cuchý, M.  2019. An Interoperable Reservation System for Public Electric Vehicle Charging Stations: A Case Study in Germany. Proceedings of the 1st ACM International Workshop on Technology Enablers and Innovative Applications for Smart Cities and Communities (TESCA'19), 22-29.}

    \cvpub{\textbf{Mrkos, J}, Komenda, A, Jakob, M.  2018. Revenue Maximization for Electric Vehicle Charging Service Providers Using Sequential Dynamic Pricing. Proc. of the 17th International Conference on Autonomous Agents and Multiagent Systems (AAMAS 2018), 832-840.}

    \cvpub{\textbf{Mrkos, J}, Komenda, A, Jakob, M.  2018. Dynamic Pricing Strategy for Electromobility using Markov Decision Processes. Proc. of the 10th International Conference on Agents and Artificial Intelligence (ICAART 2018), 507-514.}

    \cvpub{\textbf{Egan, M}, Drchal, J, Mrkos, J, Jakob, M.  2018. Towards Data-Driven On-Demand Transport. EAI Endorsed Transactions on Industrial Networks and Intelligent Systems, 5(14).}
    
    
    % \cvpub{\textbf{Name, Y}, Author Two, Author Three, Author Four, Author Five. 2017. Title of our fancy paper, which has a very long name to demonstrate what happens when this goes onto two lines. Title of the Journal, 2(1): 1000-1100.}

    % \cvpub{\textbf{Name, Y}, Author Two, Author Three. 2016. Title of our other fancy paper, which also has a very long name so that the citation goes onto the next line. Journal, 1(1): 1000-1100.}
\end{cvpubs}


% % %---------------------------------------------------------
% \cvsubsection{Accepted}
% % %---------------------------------------------------------

% \begin{cvpubs}


% \end{cvpubs}

% %---------------------------------------------------------
\cvsubsection{In Review}
% %---------------------------------------------------------

\begin{cvpubs}
    \cvpub{\textbf{Fiedler, D}, Difonzo, F, Mrkos, J. 2024. Optimal Chaining of Vehicle Plans with Time Windows. In review in "IEEE Transactions on Intelligent Transportation Systems". Preprint at \hrefs{http://arxiv.org/abs/2401.02873}{arXiv:2401.02873}}
\end{cvpubs}

% % %---------------------------------------------------------
% \cvsubsection{In Prep}
% % %---------------------------------------------------------

% \begin{cvpubs}
% \small \color{black}
%     \cvpub{Mrkos, J}, Jakob, M. Dynamic Pricing in Network Revenue Management with MDP models and MCTS. 
% \end{cvpubs}

% % %---------------------------------------------------------
% \cvsubsection{Reports}
% % %---------------------------------------------------------

% \begin{cvpubs}
%     \cvpub{\textbf{Cuchý, M}, Fiedler, D, Mrkos, J, Vokřínek, J.  2021. Feasibility of VTOL Transport in Urban Environments. Bell Textron Multi-Modal Traveler Modeling Project.}

%     \cvpub{\textbf{Mrkos, J}, Drchal, J, Egan, M, Jakob, M.  2016. Liftago On-Demand Transport Dataset and Market Formation Algorithm Based on Machine Learning. Liftago Market Formation Project. Available at \hrefs{https://arxiv.org/abs/1608.02858}{arXiv:1608.02858}.}
% \end{cvpubs}

% % %---------------------------------------------------------
